---
title: "Experiment 2 data visualization"
output: word_document
---

## Load packages

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("helpers.R")
library(tidyverse)
library(lme4)
library(wesanderson)

theme_set(theme_bw())
```

## Load the data

Note: if you have not run the data cleaning code, then the .zip file with clean data must be unzipped before running this code.
```{r}
et_data <- read.csv("../data/clean_data.csv", stringsAsFactors = TRUE)
```

## Test trials analysis

We want to examine the test trials, specifically during the event stage when participants hear the ambiguous word and see both images. We exclude looks that aren't to one of the two images.
```{r}
test_data <- et_data %>% filter(target_audio_type == "novel",
                                trial_stage == "event",
                                look_left_img == TRUE | 
                                  look_right_img == TRUE)
```

Also, add trial number:
```{r}
test_data <- test_data %>% mutate(trial_name = case_when(
  trial_no == 9 ~ "Trial 9",
  trial_no == 10 ~ "Trial 10",
  trial_no == 11 ~ "Trial 11",
  trial_no == 12 ~ "Trial 12"
))

test_data$trial_name <- factor(test_data$trial_name, levels = c("Trial 9", "Trial 10", "Trial 11", "Trial 12"))
```

Pull out looks after the disambiguation point of the syntactic frame.
```{r}
test_data_event <- test_data %>% 
  filter(time_since_trial_start >= trial_frame_start & 
           time_since_trial_start <=  trial_frame_start + 9000)
```

Add a column for proportion of looks to the action image on each test trial. We will only examine proportion of looks to the action image, since the proportion of looks to the object image is simply 1 - (proportion of looks to the action image).
```{r}
test_data_event <- test_data_event %>% group_by(participant_id, trial_no) %>% mutate(trial_prop_action = mean(look_action_img))
```

Make a data frame with only one row per participant trial:
```{r}
test_data_uniq <- test_data_event %>% 
  group_by(participant_id, trial_no) %>%
  filter(row_number() == 1) %>% group_by(participant_id) %>%
  mutate(subj_prop_action = mean(trial_prop_action))
```

We also do this for the left and right videos (which we will use for sanity checks).
```{r}
test_data_event <- test_data_event %>% group_by(participant_id, trial_no) %>%
  mutate(trial_prop_left = mean(look_left_img),
         trial_prop_right = mean(look_right_img))
```


### Proportion of looks to the left and right videos

Before we go on to the main analysis, we want to verify that there is not a bias toward looking to the left or right videos.

Calculate confidence intervals for the mean proportion of looks to the left and right videos.
```{r}
test_left_right <- test_data_event %>% group_by(participant_id) %>%
  summarise(left = mean(trial_prop_left),
            right = mean(trial_prop_right)) %>%
  gather(screen_side, mean_prop_looks, left:right, 
         factor_key = TRUE) %>%
  group_by(screen_side) %>% 
  summarise(side_prop_looks = mean(mean_prop_looks),
            CI.low = ci.low(mean_prop_looks),
            CI.high = ci.high(mean_prop_looks)) %>%
  mutate(YMin = side_prop_looks - CI.low, 
         YMax = side_prop_looks + CI.high)
```

Graph the mean proportion of looks to the left and right images.
```{r}
ggplot(test_left_right) +
  aes(x = screen_side, y = side_prop_looks, fill = screen_side) +
  geom_bar(stat = "identity") +
  ggtitle("Test trials: Mean proportion of looks to left and right images") +
  xlab("Screen side") +
  ylab("Proportion of looks") +
  geom_errorbar(aes(ymin = YMin, ymax = YMax), width = .25) +
  scale_fill_manual(name="Screen side",
                    values=wes_palette("Royal1")[1:2])
ggsave(file="../graphs/prop_looks_left_right.pdf",width=5.5,height=4)
```

There is not a significant difference in the proportion of looks to the left and right images. This is what we would expect.

### Proportion of looks based on order

We had two possible orders that determined whether participants saw the action image or the object image first on each trial. Note that each order was counterbalanced for which image appeared first and which side of the screen it appeared on, so we do not expect this to affect the proportion of looks.

Calculate confidence intervals for the mean proportion of looks to the action video based on participant order.
```{r}
order_sum <- test_data_uniq %>% group_by(img_side_order) %>% 
summarise(order_prop_action = mean(subj_prop_action),
          CI.Low = ci.low(subj_prop_action),
          CI.High = ci.high(subj_prop_action)) %>%
  mutate(YMin = order_prop_action - CI.Low, 
         YMax = order_prop_action + CI.High)
```

Graph these confidence intervals.
```{r}
ggplot(order_sum) +
  aes(x = img_side_order, y = order_prop_action, fill = img_side_order) +
  geom_bar(stat = "identity") +
  scale_fill_manual(name = "Order",values = wes_palette("Royal1")[1:2],
                    labels = c("order 1", "order 2")) +
  ggtitle("Test trials: Mean proportion of looks to action image based on order") +
  xlab("Order") +
  ylab("Mean proportion of looks") +
  geom_point(data = test_data_uniq, aes(x = img_side_order, y = subj_prop_action),
             shape = 21, size = .3) +
  geom_errorbar(data = order_sum, 
                aes(ymin = YMin, ymax = YMax), width = .25)
ggsave(file="../graphs/prop_looks_order.pdf",width=6,height=4)
```
There may be a difference in mean proportion of looks to action image based on order.


### Proportion of looks to the action video: Test trials

This is our main measure of interest: the proportion of looks to the action video on test trials. We expect participants in the verb condition to have a higher proportion of looks to the action video.

Calculate confidence intervals for the mean proportion of looks to the action image by condition.
```{r}
test_action_sum <- test_data_uniq %>% group_by(participant_id) %>% 
  filter(row_number() == 1) %>% group_by(condition) %>%
  # note: we pull out only the first row because each subject only has ONE mean calculated across all four test trials and we don't want to quadruple-count each data point
summarise(cond_prop_action = mean(subj_prop_action),
          sd = sd(subj_prop_action),
          CI.Low = ci.low(subj_prop_action),
          CI.High = ci.high(subj_prop_action), 
          n = n()) %>%
  mutate(YMin = cond_prop_action - CI.Low, 
         YMax = cond_prop_action + CI.High)
```

Then, we can make a plot with the confidence intervals as well as individual dots to represent each participant's mean proportion of looks to the action video.
```{r}
ggplot(test_action_sum) +
  aes(x = condition, y = cond_prop_action, fill = condition) +
  geom_bar(stat = "identity") +
  scale_fill_manual(name = "Condition",values = c(wes_palette("Royal1")[1], wes_palette("Royal1")[2], "dodgerblue3")) +
  ggtitle("Test trials: Participants' mean proportion of looks to action image") +
  xlab("Condition") +
  ylab("Mean proportion of looks") +
  geom_point(data = test_data_uniq, aes(x = condition, y = subj_prop_action),
             shape = 21, size = .3) +
  geom_errorbar(data = test_action_sum, 
                aes(ymin = YMin, ymax = YMax), width = .25)
ggsave(file="../graphs/prop_looks_test.pdf",width=6,height=4)
```

Summarize proportion looking by trial number.
```{r}
test_action_sum_trial <- test_data_uniq %>% 
  group_by(condition, trial_name) %>% 
summarise(cond_prop_action = mean(trial_prop_action),
          sd = sd(trial_prop_action),
          CI.Low = ci.low(trial_prop_action),
          CI.High = ci.high(trial_prop_action),
          n = n()) %>%
  mutate(YMin = cond_prop_action - CI.Low, 
         YMax = cond_prop_action + CI.High)
```


Graph proportion looking by trial number.
```{r}
ggplot(test_action_sum_trial) +
  aes(x = condition, y = cond_prop_action, fill = condition) +
  geom_bar(stat = "identity") +
   facet_wrap(trial_name ~ .) +
  scale_fill_manual(name = "Condition",values = c(wes_palette("Royal1")[1], wes_palette("Royal1")[2], "dodgerblue3")) +
  ggtitle("Test trials: Participants' mean proportion of looks to action image") +
  xlab("Condition") +
  ylab("Mean proportion of looks") +
  geom_point(data = test_data_uniq, aes(x = condition, y = trial_prop_action),
             shape = 21, size = .3) +
  geom_errorbar(data = test_action_sum_trial, 
                aes(ymin = YMin, ymax = YMax), width = .25)
ggsave(file="../graphs/prop_looks_test_trial.pdf",width=6,height=4)
```

Summarize proportion looking by image pair name.
```{r}
test_action_sum_item <- test_data_uniq %>% 
  group_by(condition, img_pair_name) %>% 
summarise(cond_prop_action = mean(trial_prop_action),
          sd = sd(trial_prop_action),
          CI.Low = ci.low(trial_prop_action),
          CI.High = ci.high(trial_prop_action),
          n = n()) %>%
  mutate(YMin = cond_prop_action - CI.Low, 
         YMax = cond_prop_action + CI.High)
```


Graph proportion looking by trial number.
```{r}
ggplot(test_action_sum_item) +
  aes(x = condition, y = cond_prop_action, fill = condition) +
  geom_bar(stat = "identity") +
   facet_wrap(img_pair_name ~ .) +
  scale_fill_manual(name = "Condition",values = c(wes_palette("Royal1")[1], wes_palette("Royal1")[2], "dodgerblue3")) +
  ggtitle("Participants' mean proportion of looks to action image by item") +
  xlab("Condition") +
  ylab("Mean proportion of looks") +
  geom_point(data = test_data_uniq, aes(x = condition, y = trial_prop_action),
             shape = 21, size = .3) +
  geom_errorbar(data = test_action_sum_item, 
                aes(ymin = YMin, ymax = YMax), width = .25)
ggsave(file="../graphs/prop_looks_test_item.pdf",width=6,height=4)
```

Group the data by accuracy.
```{r}
test_data_uniq <- test_data_uniq %>% mutate(accuracy_group = case_when(
  accuracy < 65 ~ "Low (50-64%)",
  accuracy >= 65 ~ "High (over 65%)"
))
```

Summarize proportion looking by accuracy.
```{r}
test_action_sum_acc <- test_data_uniq %>% group_by(participant_id) %>% 
  filter(row_number() == 1) %>%
  group_by(condition, accuracy_group) %>% 
summarise(cond_prop_action = mean(subj_prop_action),
          sd = sd(subj_prop_action),
          CI.Low = ci.low(subj_prop_action),
          CI.High = ci.high(subj_prop_action), 
          n = n()) %>%
  mutate(YMin = cond_prop_action - CI.Low, 
         YMax = cond_prop_action + CI.High)
```

Graph the data by accuracy.
```{r}
ggplot(test_action_sum_acc) +
  aes(x = condition, y = cond_prop_action, fill = condition) +
  geom_bar(stat = "identity") +
   facet_wrap(accuracy_group ~ .) +
  scale_fill_manual(name = "Condition",values = c(wes_palette("Royal1")[1], wes_palette("Royal1")[2], "dodgerblue3")) +
  ggtitle("Test trials: Participants' mean proportion of looks to action image by accuracy group") +
  xlab("Condition") +
  ylab("Mean proportion of looks") +
  geom_point(data = test_data_uniq, aes(x = condition, y = subj_prop_action),
             shape = 21, size = .3) +
  geom_errorbar(data = test_action_sum_acc, 
                aes(ymin = YMin, ymax = YMax), width = .25)
ggsave(file="../graphs/prop_looks_test_acc.pdf",width=8,height=4)
```

There do not seem to be large differences based on accuracy.


### Time course

Get mean times when "the girls" ends and the novel word ends.
```{r}
girls_end = mean(test_data_uniq$frame_end - test_data_uniq$frame_start)
novel_word_end = mean(test_data_uniq$novel_word_end - test_data_uniq$frame_start)
```

Make a new column for time since naming event.
```{r}
test_data <- test_data %>% 
  mutate(time_since_disambig = time_since_trial_start - trial_frame_start)
```

Separate the data into timebins.
```{r}
test_data_timecourse <- test_data %>% filter(time_since_disambig <= 6250) %>%
  mutate(timebin = plyr::round_any(time_since_disambig, 50))
```

Plot the timecourse data by trial number.
```{r}
prop_action_timecourse_sum_trial <- test_data_timecourse %>% 
  group_by(timebin, condition, trial_name) %>% 
  summarise(timebin_prop_action = mean(look_action_img))
```

Make the graph.
```{r}
ggplot(prop_action_timecourse_sum_trial) +
  aes(x = timebin, y = timebin_prop_action, color = condition) +
  geom_point(size = .2) +
  geom_smooth(size = .2) +
  facet_grid(trial_name ~ .) +
  ggtitle("Proportion of looks to action image on test trials") +
  xlab("Time since syntactic frame disambiguation (ms) during event phase") +
  ylab("Mean proportion of looks") +
  scale_color_manual(name="Condition", values = c(wes_palette("Royal1")[1], wes_palette("Royal1")[2], "dodgerblue3")) +
  geom_hline(yintercept = .5, linetype = "dashed") +
  geom_vline(xintercept = 0) +
  geom_vline(xintercept = girls_end, linetype = "dashed") +
  geom_vline(xintercept = novel_word_end, linetype= "dotted")
  #geom_errorbar(data = prop_action_timecourse_sum_trial, aes(ymin = YMin, ymax = YMax), width = .25, position = position_dodge(width = 60), alpha = .4)
ggsave(file="../graphs/naming_timecourse_trial_smooth.pdf",width=8,height=6)
```

Plot the timecourse collapsing by trial number.
```{r}
prop_action_timecourse_sum <- test_data_timecourse %>% 
  group_by(timebin, condition) %>% 
  summarise(timebin_prop_action = mean(look_action_img))
```

Make the plot.
```{r}
ggplot(prop_action_timecourse_sum) +
  aes(x = timebin, y = timebin_prop_action, color = condition) +
  geom_point(size = .3) +
  geom_smooth() +
  ggtitle("Exp 2 time course: Proportion of looks to action image on test trials") +
  xlab("Time since onset of ambiguous syntactic frame (ms)") +
  ylab("") +
  scale_color_manual(name="Condition", values = c(wes_palette("Royal1")[1], wes_palette("Royal1")[2], "dodgerblue3")) +
  geom_hline(yintercept = .5, linetype = "dashed") +
  geom_vline(xintercept = 0, colour = "black") +
  # mean end of 'the g-'
  geom_vline(xintercept = girls_end, linetype = "dashed") +
  # mean end of 'the girls'
  geom_vline(xintercept = novel_word_end, linetype= "dotted") +
  # mean end of novel word
  scale_x_continuous(breaks = seq(min(prop_action_timecourse_sum$timebin), 
                                  max(prop_action_timecourse_sum$timebin), by = 1000))
ggsave(file="../graphs/timecourse_smooth.pdf",width=8,height=5)
```


## Training trials analysis

We can analyze the training trial data to confirm that participants are looking at the video that is described.

Select the training trials only (not including the filler trials).
```{r}
train_data <- et_data %>% filter(target_audio_type != "novel",
                                look_left_img == TRUE | 
                                  look_right_img == TRUE)
```

Also, add trial number:
```{r}
train_data <- train_data %>% mutate(trial_name = case_when(
  trial_no == 1 ~ "Trial 1",
  trial_no == 2 ~ "Trial 2",
  trial_no == 3 ~ "Trial 3",
  trial_no == 4 ~ "Trial 4",
  trial_no == 5 ~ "Trial 5",
  trial_no == 6 ~ "Trial 6",
  trial_no == 7 ~ "Trial 7",
  trial_no == 8 ~ "Trial 8"
))

train_data$trial_name <- factor(train_data$trial_name, levels = c("Trial 1", "Trial 2", "Trial 3", "Trial 4", "Trial 5", "Trial 6", "Trial 7", "Trial 8"))
```

### Looks to action image during event stage

First, we examine the event stage, which is when participants hear the descriptor. Participants in the verb condition hear a phrase with a verb, while participants in the noun condition hear a phrase with a noun.
```{r}
train_event <- train_data %>% 
  filter(trial_stage == "event")
```

Add a column for proportion of looks to the action image on each trial.
```{r}
train_event <- train_event %>% 
  group_by(participant_id, trial_no) %>% 
  mutate(trial_prop_action = mean(look_action_img))

train_event_uniq <- train_event %>% 
  group_by(participant_id, trial_no) %>%
  filter(row_number() == 1) %>% group_by(participant_id, trial_type) %>%
  mutate(subj_prop_action = mean(trial_prop_action))
```

Calculate confidence intervals for the mean proportion of looks to the action image by condition.
```{r}
train_action_sum <- train_event_uniq %>% 
  group_by(participant_id, trial_type) %>% 
  filter(row_number() == 1) %>% group_by(condition, trial_type) %>%
summarise(cond_prop_action = mean(subj_prop_action),
          sd = sd(subj_prop_action),
          CI.Low = ci.low(subj_prop_action),
          CI.High = ci.high(subj_prop_action), 
          n = n()) %>%
  mutate(YMin = cond_prop_action - CI.Low, 
         YMax = cond_prop_action + CI.High)
```

Then, we can make a plot with the confidence intervals as well as individual dots to represent each participant's mean proportion of looks to the action video.
```{r}
ggplot(train_action_sum) +
  aes(x = trial_type, y = cond_prop_action, fill = condition) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_fill_manual(name = "Condition",values = c(wes_palette("Royal1")[1], wes_palette("Royal1")[2], "dodgerblue3")) +
  ggtitle("Training trials: Participants' mean proportion of looks to action image") +
  xlab("Condition") +
  ylab("Mean proportion of looks") +
  geom_errorbar(data = train_action_sum, 
                aes(ymin = YMin, ymax = YMax), position = position_dodge(0.9), width = .25)
ggsave(file="../graphs/prop_looks_train.pdf",width=6,height=4)
```

Summarize proportion looking by trial number.
```{r}
train_action_sum_trial <- train_event_uniq %>% 
  group_by(condition, trial_name, trial_type) %>% 
summarise(cond_prop_action = mean(trial_prop_action),
          sd = sd(trial_prop_action),
          CI.Low = ci.low(trial_prop_action),
          CI.High = ci.high(trial_prop_action),
          n = n()) %>%
  mutate(YMin = cond_prop_action - CI.Low, 
         YMax = cond_prop_action + CI.High)
```

Graph proportion looking by trial number.
```{r}
ggplot(train_action_sum_trial) +
  aes(x = trial_type, y = cond_prop_action, fill = condition) +
  geom_bar(stat = "identity", position = "dodge") +
   facet_wrap(trial_name ~ .) +
  scale_fill_manual(name = "Condition",values = c(wes_palette("Royal1")[1], wes_palette("Royal1")[2], "dodgerblue3")) +
  ggtitle("Test trials: Participants' mean proportion of looks to action image") +
  xlab("Condition") +
  ylab("Mean proportion of looks") +
  geom_point(data = train_event_uniq, aes(x = trial_type, y = trial_prop_action),
             shape = 21, size = .3) +
  geom_errorbar(data = train_action_sum_trial, 
                aes(ymin = YMin, ymax = YMax), width = .25) +
  theme(axis.text.x = element_text(angle = 60, hjust = 1))
  
ggsave(file="../graphs/prop_looks_train_trial.pdf",width=6,height=4)
```

Look at just the first few trials.

Summarize proportion looking by trial number.
```{r}
train_action_sum_trial_sm <- train_event_uniq %>% filter(trial_no <= 4) %>%
  group_by(condition, trial_name, trial_type) %>% 
summarise(cond_prop_action = mean(trial_prop_action),
          sd = sd(trial_prop_action),
          CI.Low = ci.low(trial_prop_action),
          CI.High = ci.high(trial_prop_action),
          n = n()) %>%
  mutate(YMin = cond_prop_action - CI.Low, 
         YMax = cond_prop_action + CI.High)
```

Graph proportion looking by trial number.
```{r}
ggplot(train_action_sum_trial_sm) +
  aes(x = trial_type, y = cond_prop_action, fill = condition) +
  geom_bar(stat = "identity", position = "dodge") +
   facet_wrap(trial_name ~ .) +
  scale_fill_manual(name = "Condition",values = c(wes_palette("Royal1")[1], wes_palette("Royal1")[2], "dodgerblue3")) +
  ggtitle("Test trials: Participants' mean proportion of looks to action image") +
  xlab("Condition") +
  theme(axis.text.x = element_text(angle = 60, hjust = 1)) +
  ylab("Mean proportion of looks") +
  geom_errorbar(data = train_action_sum_trial_sm, 
                aes(ymin = YMin, ymax = YMax), width = .25, position = position_dodge(0.75))
ggsave(file="../graphs/prop_looks_initial_train_trial.pdf",width=6,height=4)
```

### Looks to action video during video previews

First, select the time periods when the video previews are playing. During the previews, only one video is playing, so we expect participants to look at the video that plays no matter what their condition is.
```{r}
preview_data <- train_data %>% filter(trial_stage == "left_preview" |
                                       trial_stage == "right_preview")
```

Add a column saying whether it is the action video preview.
```{r}
preview_data <- preview_data %>% 
  mutate(action_preview = (trial_stage == "left_preview" & 
                             action_img == "left") |
           (trial_stage == "right_preview" &
              action_img == "right"))
```

Add a column for proportion of looks on each training trial.
```{r}
preview_data <- preview_data %>% group_by(participant_id, trial_no, action_preview) %>% mutate(trial_prop_action = mean(look_action_img),
         trial_prop_object = mean(look_object_img))
```

Make a data frame with one row per participant per trial, and add a column for each participant's proportion of looks across the four training trials.
```{r}
preview_data_uniq = preview_data %>% 
  group_by(participant_id, action_preview, trial_no) %>%
  filter(row_number() == 1) %>%
  mutate(subj_prop_action = mean(trial_prop_action),
         subj_prop_object = mean(trial_prop_object))
```

Calculate confidence intervals for the mean proportion of looks to the action and object videos by condition.
```{r}
preview_sum <- preview_data_uniq %>% 
  group_by(participant_id, action_preview) %>% 
  filter(row_number() == 1) %>%
  group_by(condition, action_preview) %>% 
  summarise(cond_prop_action = mean(subj_prop_action),
            CI.Low = ci.low(subj_prop_action),
            CI.High = ci.high(subj_prop_action),
            n = n()) %>%
  mutate(YMin = cond_prop_action - CI.Low, 
         YMax = cond_prop_action + CI.High)
```

Graph the proportion of looks toward the action video when it is the only video playing.
```{r}
ggplot(preview_sum) +
  aes(x = action_preview, y = cond_prop_action, fill = condition) +
  geom_bar(stat = "identity", position = "dodge") +
  ggtitle("Training trials: Mean proportion of looks during image previews") +
  xlab("Type of image preview") +
  ylab("Mean proportion of looks") +
  scale_fill_manual(name="Condition",values = c(wes_palette("Royal1")[1], wes_palette("Royal1")[2], "dodgerblue3")) +
  scale_x_discrete(labels = c("Object image", "Action image")) +
  geom_errorbar(aes(ymin = YMin, ymax = YMax), width = .25, 
                position = position_dodge(width = .9))
ggsave(file="../graphs/prop_looks_train_preview.pdf",width=6,height=4)
```

We see no difference in looking patterns by condition, which reassures us that the eye-tracker is in fact measuring which image participants are looking at.

## Filler trials analysis

On filler trials, we expect the pattern to be reversed: Participants in the noun condition should look more at the action video, and participants in the verb condition should look more at the object video.

```{r}
filler_data <- et_data %>% filter(target_audio_type == "noun_filler" |
                                    target_audio_type == "verb_filler",
                                  trial_stage == "event",
                                  look_left_img == TRUE | 
                                  look_right_img == TRUE)
```

Add a column for proportion of looks on each training trial.
```{r}
filler_data <- filler_data %>% group_by(participant_id, trial_no) %>% mutate(trial_prop_action = mean(look_action_img))
```

Add a column for each participant's mean proportion of looks across the four training trials.
```{r}
filler_data_uniq <- filler_data %>% 
  group_by(participant_id, trial_no) %>%
  filter(row_number() == 1) %>%
  group_by(participant_id) %>%
  mutate(subj_prop_action = mean(trial_prop_action))
```

Calculate confidence intervals for the mean proportion of looks to the action video by condition.
```{r}
filler_sum <- filler_data_uniq %>% group_by(participant_id) %>%
  filter(row_number() == 1) %>%
  group_by(condition) %>% 
summarise(cond_prop_action = mean(subj_prop_action),
          sd = sd(subj_prop_action),
          CI.Low = ci.low(subj_prop_action),
          CI.High = ci.high(subj_prop_action),
          n = n()) %>%
  mutate(YMin = cond_prop_action - CI.Low, 
         YMax = cond_prop_action + CI.High)
```

Graph these confidence intervals, and add individual dots to represent each participant's mean proportion of looks to the action video.
```{r}
ggplot(filler_sum) +
  aes(x = condition, y = cond_prop_action, fill = condition) +
  geom_bar(stat = "identity") +
  scale_fill_manual(name = "Condition",values = c(wes_palette("Royal1")[1], wes_palette("Royal1")[2], "dodgerblue3")) +
  ggtitle("Filler trials: Mean proportion of looks to action video") +
  xlab("Condition") +
  ylab("Mean proportion of looks") +
  geom_point(data = filler_data_uniq, aes(x = condition, y = subj_prop_action),
             shape = 21, size = .3) +
  geom_errorbar(data = filler_sum, 
                aes(ymin = YMin, ymax = YMax), width = .25)
ggsave(file="../graphs/prop_looks_filler.pdf",width=6,height=4)
```

As expected, participants in the noun condition are looking more at the action video and participants in the verb condition are looking more at the object video.


## Selecting an image

Gather names of action and object images.
```{r}
object_imgs = c("shoe", "doll", "hat", "ball", "book", "dog", "box", "horse", "vash_noun", "dax_noun", "smick_noun", "nup_noun", "fep_noun")
action_imgs = c("read", "drink", "wave", "cry", "sit", "eat", "sleep", "draw", "vash_verb", "dax_verb", "smick_verb", "nup_verb", "fep_verb")
```

Add a column stating whether participants selected the object or action image on the last trial.
```{r}
et_data <- et_data %>% mutate(clicked_img_type = case_when(
  clicked_img %in% object_imgs ~ "object",
  clicked_img %in% action_imgs ~ "action",
))
```

Count the number of participants who selected each image type by condition.
```{r}
clicked_img_sum <- et_data %>% group_by(condition, clicked_img_type) %>% 
  summarise(n = length(unique(participant_id))) %>% filter(!is.na(clicked_img_type))

clicked_img_sum <- clicked_img_sum %>% group_by(condition) %>% mutate(total = sum(n))

clicked_img_sum <- clicked_img_sum %>% 
  mutate(proportion = n/total,
         CI.Low = proportion + 1.96*sqrt(proportion*(1-proportion)/total),
         CI.High = proportion - 1.96*sqrt(proportion*(1-proportion)/total))
```

Pull out just proportion of looks to action image:
```{r}
clicked_img_sum = clicked_img_sum %>% filter(clicked_img_type == "action")
```

Graph the proportion of participants who selected each image type by condition.
```{r}
ggplot(clicked_img_sum) +
  aes(x = condition, y = proportion, fill = condition) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_fill_manual(name = "Condition",values = c(wes_palette("Royal1")[1:2], "dodgerblue3")) +
  ggtitle("Proportion selecting action image on explicit selection trial") +
  xlab("Condition") +
  ylab("Proportion of participants") +
  geom_errorbar(data = clicked_img_sum, 
                aes(ymin = CI.Low, ymax = CI.High),
                position = position_dodge(width = .9), width=.2)
ggsave(file="../graphs/prop_clicked_img.pdf",width=6,height=4)
```

### Looks before and after syntactic frame

Calculate the proportion of looks to the action image before the end of 'The g-' vs. after, so we can see if there is a difference:
```{r}
diff_prop_action_data <- test_data %>% group_by(participant_id, trial_no) %>%
  filter(time_since_trial_start <= trial_frame_start + 9000) %>%
  mutate(pre_frame_prop = mean(na.omit(look_action_img[time_since_trial_start < trial_frame_start])), # before frame
         post_frame_prop = mean(na.omit(look_action_img[time_since_trial_start >= trial_frame_start]))) # after frame
```

Calculate the difference in looks before vs. after the end of 'The g-':
```{r}
diff_prop_action_data = diff_prop_action_data %>% 
  group_by(participant_id, trial_no) %>%
  mutate(trial_diff_prop_action = post_frame_prop - pre_frame_prop) %>%
  filter(row_number() == 1)
```

Calculate each participant's average difference in action image proportion looking time across test trials.
```{r}
diff_prop_action_data = diff_prop_action_data %>% 
  group_by(participant_id) %>% 
  mutate(subj_diff_prop_action = mean(trial_diff_prop_action))

diff_prop_action_data = diff_prop_action_data %>% mutate(girls_end = girls_end, novel_word_end = novel_word_end)
```

Summarize:
```{r}
diff_prop_action_sum = diff_prop_action_data %>% 
  group_by(participant_id) %>%
  filter(row_number() == 1) %>% 
  group_by(condition) %>% 
  summarise(sd = sd(na.omit(subj_diff_prop_action)),
            cond_diff_prop_action = mean(na.omit(subj_diff_prop_action)),
            CI.Low = ci.low(na.omit(subj_diff_prop_action)),
            CI.High = ci.high(na.omit(subj_diff_prop_action)),
            n = n())  %>%
              mutate(YMin = cond_diff_prop_action - CI.Low, 
                     YMax = cond_diff_prop_action + CI.High)
```

Graph the difference in proportion looking to action image before the structure vs. after.
```{r}
ggplot(diff_prop_action_sum) +
  aes(x = condition, y = cond_diff_prop_action, fill = condition) +
  geom_bar(stat = "identity") +
  scale_fill_manual(name = "Condition",values = c(wes_palette("Royal1")[1], wes_palette("Royal1")[2], "dodgerblue3")) +
  ggtitle("Adults: Difference in mean proportion of looks to action image") +
  xlab("Condition") +
  ylab(" Diff. in mean prop. of looks before vs. after syntactic frame") +
 geom_point(data = diff_prop_action_data, aes(x = condition, y = subj_diff_prop_action), shape = 21, size = .5) +
  geom_errorbar(data = diff_prop_action_sum, 
                aes(ymin = YMin, ymax = YMax), width = .25)
ggsave(file="../graphs/diff_prop_action.pdf",width=6,height=4)
```

Save the dataframe with information about proportion of looks to the action image before hearing "The g-" vs. after:
```{r}
write.csv(diff_prop_action_data, "../data/diff_prop_action_data.csv")
write.csv(diff_prop_action_data, "../../4_all_experiments/data/exp2_diff_prop_action.csv")
```

