---
title: "Experiment 2 data analysis"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("helpers.R")
library(lme4)
library(dplyr)
library(tidyverse)
library(MuMIn)
library(languageR)
library(emmeans)
library(lmerTest)
```

## Load the data

Note: the zip file with clean data must be unzipped before running this code.
```{r}
et_data <- read.csv("../data/clean_data.csv", stringsAsFactors = TRUE)
```


## Inspect the data

Check the number of participants in each order and condition.
```{r}
et_data %>% group_by(condition) %>% 
  summarise(n = length(unique(participant_id)))
```

The number of participants is distributed relatively equally between the two orders and the two conditions.

Check the gender of participants.
```{r}
et_data %>% group_by(gender) %>% 
  summarise(n = length(unique(participant_id)))
```

Check how much data we retain when we only count looks to the action image or the object image.
```{r}
length(et_data$x[et_data$look_left_img == TRUE | 
                   et_data$look_right_img == TRUE]) / length(et_data$x)
```

We retain about 62% of the data. The high rate of track loss is not surprising given how noisy online eye-tracking is.


## Pull out the test data

We want to examine the test trials, specifically when they are at the event stage and after the disambiguating syntactic frame.
```{r}
test_data <- et_data %>% filter(target_audio_type == "novel",
                                trial_stage == "event",
                                look_left_img == TRUE | 
                                  look_right_img == TRUE,
                                time_since_trial_start >= trial_frame_start,
                                time_since_trial_start <= 26300)
```

Add a column for proportion of looks on each test trial.
```{r}
test_data <- test_data %>% group_by(participant_id, trial_no) %>% mutate(trial_prop_action = mean(look_action_img))
```


## Linear regression


### Transforming proportion of looks

First, let's make a quick histogram of the values for proportion of looks to the action image.
```{r}
hist(unique(test_data$trial_prop_action),
            main = "Histogram of proportion of looks to action image",
            xlab = "Proportion of looks to action image")
```

We see that the values are quite spread out. We will repeat the original authors' analysis, in which they ArcSin-transform the proportion of looks to the action video.

Add a column with ArcSin-transformed proportion of looks toward the action video for each trial.
```{r}
test_data <- test_data %>% 
  mutate(arcsin_prop_action = asin(sqrt((trial_prop_action))))
```

The histogram of the transformed proportions looks much more normal.
```{r}
hist(unique(test_data$arcsin_prop_action),
     main = "Histogram of ArcSin-transformed proportion of looks to action image",
            xlab = "ArcSin-transformed proportion of looks to action image")
```


### Regression model

Make a data frame with just one row per participant per trial, and calculate each participant's average proportion of looks to the action image over all the trials.
```{r}
test_data_uniq <- test_data %>% group_by(participant_id, trial_no) %>%
  filter(row_number() == 1) %>% group_by(participant_id) %>%
  mutate(subj_prop_action = mean(trial_prop_action))
```

Now, we build a mixed effects linear model regressing ArcSin-transformed proportion of looks on condition, with a random intercept for participant.
```{r}
lin <- lmer(arcsin_prop_action ~ condition + (1|participant_id), 
            data = test_data_uniq, REML = F)
summary(lin)
```


It looks like the intercept and condition are highly correlated. Try centering condition:
```{r}
test_data_uniq$center_condition <- myCenter(test_data_uniq$condition)
```

Now, we rerun the linear regression.
```{r}
lin.cen <- lmer(arcsin_prop_action ~ center_condition + (1|participant_id), 
            data = test_data_uniq, REML = F)
summary(lin.cen)
```

This takes care of the collinearity.

Now, we conduct a likelihood ratio test between the mixed effects linear regression model and the model without the effect of condition:
```{r}
lin.base <- lmer(arcsin_prop_action ~ (1|participant_id), data = test_data_uniq, 
                 REML = F)
summary(lin.base)

anova(lin.cen, lin.base)
```

There is a significant main effect of condition on proportion of looks to the action image.

## Logistic regression

Now we build a mixed effects logistic regression model predicting log odds of looking towards the action video over looking towards the object video as a function of condition, with random intercepts for participant and previous look.
```{r}
lg <- glmer(look_action_img ~ condition + 
              previous_look_action_img + 
              (1 + previous_look_action_img | participant_id), 
             data = test_data,
             family = "binomial")
summary(lg)
```


There is a high correlation between condition and the intercept as well as previous look and the intercept, so we center condition and previous look.
```{r}
test_data$center_condition <- myCenter(test_data$condition)
test_data$center_prev_look_action <- myCenter(as.numeric(test_data$previous_look_action_img))

lg.cen <- glmer(look_action_img ~ center_condition + center_prev_look_action + 
              (1 + center_prev_look_action | participant_id), 
             data = test_data,
             family = "binomial")
summary(lg.cen)
```

This reduces the collinearity.

Now, we conduct a likelihood ratio test between the logistic regression model and the model without the effect of condition:
```{r}
lg.base.con <- glmer(look_action_img ~ previous_look_action_img + 
              (1 + previous_look_action_img | participant_id), 
             data = test_data,
             family = "binomial")
summary(lg.base.con)

anova(lg.base.con, lg)
```

There is a significant main effect of condition such that participants in the verb condition were more likely to look to the action video. 

We also conduct a likelihood ratio test between the logistic regression model and the model without the effect of previous gaze:
```{r}
lg.base.prev <- glmer(look_action_img ~ center_condition + 
              (1 | participant_id), 
             data = test_data,
             family = "binomial")
summary(lg.base.prev)

anova(lg.base.prev, lg.cen)
```

There is a significant main effect of previous look such that if a participant's previous look was to the action video, their next look is more likely to be to the action video as well.

## Regression model of difference in proportion of looks

Load data on difference in proportion looks to action image before vs. after hearing "The g-":
```{r}
diff_prop_action_data = read.csv("../data/diff_prop_action_data.csv", stringsAsFactors = TRUE)
```

Run a linear regression of difference in proportion looks:
```{r}
diff.lin <- lmer(trial_diff_prop_action ~ condition + (1|participant_id), 
            data = diff_prop_action_data, REML= F)
summary(diff.lin)
```

Now, we conduct a likelihood ratio test between the logistic regression model and the model without the effect of condition:
```{r}
diff.base <- lmer(trial_diff_prop_action ~ (1|participant_id), 
            data = diff_prop_action_data, REML= F)
summary(diff.base)

anova(diff.base, diff.lin)
```

Rerun the linear regression with the noun condition as the baseline:
```{r}
diff_prop_action_data$condition_noun_bl = relevel(diff_prop_action_data$condition, ref = "noun")

diff.lin.noun <- lmer(trial_diff_prop_action ~ condition_noun_bl + (1|participant_id), 
            data = diff_prop_action_data, REML= F)
summary(diff.lin.noun)
```

