---
title: "Experiment 3 data analysis"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("helpers.R")
library(lme4)
library(dplyr)
library(tidyverse)
library(MuMIn)
library(emmeans)
library(lmerTest)
```

## Set-up

Read in data file:
```{r}
event_data_disambig = read.csv("../data/full_test_data_for_analysis.csv", stringsAsFactors = TRUE)
```

Check the number of participants in each condition.
```{r}
event_data_disambig %>% group_by(condition) %>% 
  summarise(n = length(unique(subid)))
```

## Transforming proportion of looks

First, let's make a quick histogram of the values for proportion of looks to the action image.
```{r}
hist(unique(event_data_disambig$trial_action_prop),
            main = "Histogram of proportion of looks to action image",
            xlab = "Proportion of looks to action image")
```

We see that the values are quite spread out. We will repeat the original authors' analysis, in which they ArcSin-transform the proportion of looks to the action video.

Add a column with ArcSin-transformed proportion of looks toward the action video for each trial.
```{r}
event_data_disambig <- event_data_disambig %>% 
  mutate(arcsin_prop_action = asin(sqrt((trial_action_prop))))
```

The histogram of the transformed proportions looks more normal.
```{r}
hist(unique(event_data_disambig$arcsin_prop_action),
     main = "Histogram of ArcSin-transformed proportion of looks to action image",
            xlab = "ArcSin-transformed proportion of looks to action image")
```

## Regression model

Make a smaller dataframe with just one row per participant per trial.
```{r}
event_data_uniq <- event_data_disambig %>% group_by(subid, trial_no) %>%
  filter(row_number() == 1) %>% group_by(subid) %>%
  mutate(subj_prop_action = mean(trial_action_prop))
```

Now, we build a mixed effects linear model regressing ArcSin-transformed proportion of looks on condition, with a random intercept for participant.
```{r}
lin <- lmer(arcsin_prop_action ~ condition + (1|subid), 
            data = event_data_uniq, REML = F)
summary(lin)
```

Now, we conduct a likelihood ratio test between the mixed effects linear regression model and the model without the effect of condition:
```{r}
lin.base <- lmer(arcsin_prop_action ~ (1|subid), data = event_data_uniq, 
                 REML = F)
summary(lin.base)

anova(lin, lin.base)
```

There is a significant main effect of condition on proportion of looks to the action image, such that participants in the noun condition have a lower proportion of looks to the action image than participants in the baseline condition.


## Logistic regression

We add columns that indicate whether the participant was looking at the action image on the previous look.
```{r}
event_data_disambig <- event_data_disambig %>% group_by(subid, trial_no) %>%
  mutate(previous_look_action_img = lag(look_action_img))
```

Now we build a mixed effects logistic regression model predicting log odds of looking towards the action video over looking towards the object video as a function of condition, with random intercepts for participant and previous look.
```{r}
lg <- glmer(look_action_img ~ condition + 
              previous_look_action_img + 
              (1 + previous_look_action_img | subid), 
             data = event_data_disambig,
             family = "binomial")
summary(lg)
```

Now, we conduct a likelihood ratio test between the logistic regression model and the model without the effect of condition:
```{r}
lg.base.con <- glmer(look_action_img ~ previous_look_action_img + 
              (1 + previous_look_action_img | subid), 
             data = event_data_disambig,
             family = "binomial")
summary(lg.base.con)

anova(lg.base.con, lg)
```

There is a significant main effect of condition such that participants in the noun condition were less likely to look to the action image than participants in the baseline condition. 

## Regression model of difference in proportion of looks

Load data on difference in proportion looks to action image before vs. after hearing "The g-":
```{r}
diff_prop_action_data = read.csv("../data/diff_prop_action_data.csv", stringsAsFactors = TRUE)
```

Run a linear regression of difference in proportion looks:
```{r}
diff.lin <- lmer(trial_diff_prop_action ~ condition + (1|subid), 
            data = diff_prop_action_data, REML= F)
summary(diff.lin)
```

Now, we conduct a likelihood ratio test between the logistic regression model and the model without the effect of condition:
```{r}
diff.base <- lmer(trial_diff_prop_action ~ (1|subid), 
            data = diff_prop_action_data, REML= F)
summary(diff.base)

anova(diff.base, diff.lin)
```
