---
title: "Experiment 1 data analysis"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("helpers.R")
library(lme4)
library(dplyr)
library(tidyverse)
library(MuMIn)
library(lmerTest)
```

## Load the data

Note: if you have not run the data cleaning code, then the .zip file with clean data must be unzipped before running this code.
```{r}
et_data <- read.csv("../data/clean_data.csv", stringsAsFactors = TRUE)
```


## Inspect the data

Check the number of participants in each order and condition.
```{r}
et_data %>% group_by(order, condition) %>% 
  summarise(n = length(unique(participant_id)))
```

The number of participants is distributed relatively equally between the two orders and the two conditions.

Check the gender of participants.
```{r}
plyr::count(et_data$gender)
et_data %>% group_by(participant_id) %>% filter(row_number() == 1) %>% 
  group_by(gender) %>% summarise(n = n())
```

Check how much data we retain when we only count looks to the action video or the object video.
```{r}
length(et_data$x[et_data$look_left_video == TRUE | 
                   et_data$look_right_video == TRUE]) / length(et_data$x)
```

## Pull out the test data

We want to examine the test trials, specifically when they are at the event stage.
```{r}
test_data <- et_data %>% filter(descriptor_condition == "test",
                                video_stage == "event",
                                look_left_video == TRUE | 
                                  look_right_video == TRUE)
```

Add a column for proportion of looks on each test trial.
```{r}
test_data <- test_data %>% group_by(participant_id, trial_no) %>% mutate(trial_prop_action = mean(look_action_video))
```


## Linear regression

### Transforming proportion of looks

First, let's make a quick histogram of the values for proportion of looks to the action video.
```{r}
hist(unique(test_data$trial_prop_action),
            main = "Histogram of proportion of looks to action video",
            xlab = "Proportion of looks to action video")
```

We see that the values are quite spread out. We will repeat the original authors' analysis, in which they ArcSin-transform the proportion of looks to the action video.

Add a column with ArcSin-transformed proportion of looks toward the action video for each trial.
```{r}
test_data <- test_data %>% 
  mutate(arcsin_prop_action = asin(sqrt((trial_prop_action))))
```

The histogram of the transformed proportions looks much more normal.
```{r}
hist(unique(test_data$arcsin_prop_action),
     main = "Histogram of ArcSin-transformed proportion of looks to action video",
            xlab = "ArcSin-transformed proportion of looks to action video")
```

### Regression model

We only need one data point per test trial per participant, so pull out this data.
```{r}
test_data_uniq <- test_data %>% group_by(participant_id, trial_no) %>%
  filter(row_number() == 1)
```

Now, we build a mixed effects linear model regressing ArcSin-transformed proportion of looks on condition, with a random intercept for participant.
```{r}
lin <- lmer(arcsin_prop_action ~ condition + (1|participant_id), 
            data = test_data_uniq, REML = F)
summary(lin)
```

It looks like the intercept and condition are highly correlated. Try centering condition:
```{r}
test_data_uniq$center_condition <- myCenter(test_data_uniq$condition)
```

Now, we rerun the linear regression.
```{r}
lin.cen <- lmer(arcsin_prop_action ~ center_condition + (1|participant_id), 
            data = test_data_uniq, REML = F)
summary(lin.cen)
```

This takes care of the collinearity.

Now, we conduct a likelihood ratio test between the mixed effects linear regression model and the model without the effect of condition:
```{r}
lin.base <- lmer(arcsin_prop_action ~ (1|participant_id), data = test_data_uniq, 
                 REML = F)
summary(lin.base)

anova(lin.cen, lin.base)
```

There is a significant main effect of condition on proportion of looks to the action video, where participants in the verb condition have a higher proportion of looks to the action video.

## Logistic regression

Now we build a mixed effects logistic regression model predicting log odds of looking towards the action video over looking towards the object video as a function of condition, with random intercepts for participant and previous look.
```{r}
lg <- glmer(look_action_video ~ condition + 
              previous_look_action_video + 
              (previous_look_action_video | participant_id), 
             data = test_data,
             family = "binomial")
summary(lg)
```


There is a high correlation between condition and the intercept as well as previous look and the intercept, so we center condition and previous look.
```{r}
test_data$center_condition <- myCenter(test_data$condition)

test_data$center_prev_look_action <- myCenter(as.numeric(test_data$previous_look_action_video))

lg.cen <- glmer(look_action_video ~ center_condition + 
                  center_prev_look_action + 
              (1 + center_prev_look_action | participant_id), 
             data = test_data,
             family = "binomial")
summary(lg.cen)
```

This reduces the collinearity.

Now, we conduct a likelihood ratio test between the logistic regression model and the model without the effect of condition:
```{r}
lg.base.con <- glmer(look_action_video ~ center_prev_look_action + 
              (1 + center_prev_look_action | participant_id), 
             data = test_data,
             family = "binomial")
summary(lg.base.con)

anova(lg.base.con, lg.cen)
```

There is a significant main effect of condition such that participants in the verb condition were more likely to look to the action video. 

We also conduct a likelihood ratio test between the logistic regression model and the model without the effect of previous gaze:
```{r}
lg.base.prev <- glmer(look_action_video ~ center_condition + 
              (1 | participant_id), 
             data = test_data,
             family = "binomial")
summary(lg.base.prev)

anova(lg.base.prev, lg.cen)
```

There is a significant main effect of previous look such that if a participant's previous look was to the action video, their next look is more likely to be to the action video as well.

## Training trials

## Pull out the training data

We want to examine the test trials, specifically when they are at the event stage.
```{r}
train_data <- et_data %>% filter(descriptor_condition == "noun" |
                                  descriptor_condition == "verb",
                                video_stage == "event",
                                look_left_video == TRUE | 
                                  look_right_video == TRUE)
```

Add a column for proportion of looks on each training trial.
```{r}
train_data <- train_data %>% group_by(participant_id, trial_no) %>% mutate(trial_prop_action = mean(look_action_video),
         trial_prop_object = mean(look_object_video))
```


## Linear regression

### Transforming proportion of looks

First, let's make a quick histogram of the values for proportion of looks to the action video.
```{r}
hist(unique(train_data$trial_prop_action),
            main = "Histogram of proportion of looks to action video",
            xlab = "Proportion of looks to action video")
```

We see that the values are quite spread out. We will repeat the original authors' analysis, in which they ArcSin-transform the proportion of looks to the action video.

Add a column with ArcSin-transformed proportion of looks toward the action video for each trial.
```{r}
train_data <- train_data %>% 
  mutate(arcsin_prop_action = asin(sqrt((trial_prop_action))))
```

The histogram of the transformed proportions looks much more normal.
```{r}
hist(unique(train_data$arcsin_prop_action),
     main = "Histogram of ArcSin-transformed proportion of looks to action video [TRAIN]",
            xlab = "ArcSin-transformed proportion of looks to action video")
```

### Regression model

We only need one data point per test trial per participant, so pull out this data.
```{r}
train_data_uniq <- train_data %>% group_by(participant_id, trial_no) %>%
  filter(row_number() == 1)
```

Now, we build a mixed effects linear model regressing ArcSin-transformed proportion of looks on condition, with a random intercept for participant.
```{r}
lin.train <- lmer(arcsin_prop_action ~ condition + (1|participant_id), 
            data = train_data_uniq, REML = F)
summary(lin.train)
```

It looks like the intercept and condition are highly correlated. Try centering condition:
```{r}
train_data_uniq$center_condition <- myCenter(train_data_uniq$condition)
```

Now, we rerun the linear regression.
```{r}
lin.train.cen <- lmer(arcsin_prop_action ~ center_condition + (1|participant_id), 
            data = train_data_uniq, REML = F)
summary(lin.train.cen)
```

This takes care of the collinearity.

Now, we conduct a likelihood ratio test between the mixed effects linear regression model and the model without the effect of condition:
```{r}
lin.train.base <- lmer(arcsin_prop_action ~ (1|participant_id), 
                       data = train_data_uniq, 
                 REML = F)
summary(lin.train.base)

anova(lin.train.cen, lin.train.base)
```

There is a significant main effect of condition on proportion of looks to the action video, where participants in the verb condition have a higher proportion of looks to the action video.

## Logistic regression

Now we build a mixed effects logistic regression model predicting log odds of looking towards the action video over looking towards the object video as a function of condition, with random intercepts for participant and previous look.
```{r}
lg.train <- glmer(look_action_video ~ condition + 
              previous_look_action_video + 
              (previous_look_action_video | participant_id), 
             data = train_data,
             family = "binomial")
summary(lg.train)
```


There is a high correlation between condition and the intercept as well as previous look and the intercept, so we center condition and previous look.
```{r}
train_data$center_condition <- myCenter(train_data$condition)

train_data$center_prev_look_action <- myCenter(as.numeric(train_data$previous_look_action_video))

lg.train.cen <- glmer(look_action_video ~ center_condition + center_prev_look_action + 
              (1 + center_prev_look_action | participant_id), 
             data = train_data,
             family = "binomial")
summary(lg.train.cen)
```

This reduces the collinearity.

Now, we conduct a likelihood ratio test between the logistic regression model and the model without the effect of condition:
```{r}
lg.train.base.con <- glmer(look_action_video ~ center_prev_look_action + 
              (1 + center_prev_look_action | participant_id), 
             data = train_data,
             family = "binomial")
summary(lg.train.base.con)

anova(lg.train.base.con, lg.train.cen)
```

There is a significant main effect of condition such that participants in the verb condition were more likely to look to the action video. 

We also conduct a likelihood ratio test between the logistic regression model and the model without the effect of previous gaze:
```{r}
lg.train.base.prev <- glmer(look_action_video ~ center_condition + 
              (1 | participant_id), 
             data = train_data,
             family = "binomial")
summary(lg.train.base.prev)

anova(lg.train.base.prev, lg.train.cen)
```

There is a significant main effect of previous look such that if a participant's previous look was to the action video, their next look is more likely to be to the action video as well.

# Filler trials

## Pull out the filler data

We want to examine the filler trials, specifically when they are at the event stage.
```{r}
filler_data <- et_data %>% filter(descriptor_condition == "noun_filler" |
                                  descriptor_condition == "verb_filler",
                                video_stage == "event",
                                look_left_video == TRUE | 
                                  look_right_video == TRUE)
```

Add a column for proportion of looks on each test trial.
```{r}
filler_data <- filler_data %>% group_by(participant_id, trial_no) %>%
  mutate(trial_prop_action = mean(look_action_video))
```


## Linear regression

### Transforming proportion of looks

First, let's make a quick histogram of the values for proportion of looks to the action video.
```{r}
hist(unique(filler_data$trial_prop_action),
            main = "Histogram of proportion of looks to action video",
            xlab = "Proportion of looks to action video")
```

We see that the values are quite spread out. We will repeat the original authors' analysis, in which they ArcSin-transform the proportion of looks to the action video.

Add a column with ArcSin-transformed proportion of looks toward the action video for each trial.
```{r}
filler_data <- filler_data %>% 
  mutate(arcsin_prop_action = asin(sqrt((trial_prop_action))))
```

The histogram of the transformed proportions looks much more normal.
```{r}
hist(unique(filler_data$arcsin_prop_action),
     main = "Histogram of ArcSin-transformed proportion of looks to action video [FILLER]",
            xlab = "ArcSin-transformed proportion of looks to action video")
```

### Regression model

We only need one data point per test trial per participant, so pull out this data.
```{r}
filler_data_uniq <- filler_data %>% group_by(participant_id, trial_no) %>%
  filter(row_number() == 1)
```

Now, we build a mixed effects linear model regressing ArcSin-transformed proportion of looks on condition, with a random intercept for participant.
```{r}
lin.fill <- lmer(arcsin_prop_action ~ condition + (1|participant_id), 
            data = filler_data_uniq, REML = F)
summary(lin.fill)
```

It looks like the intercept and condition are highly correlated. Try centering condition:
```{r}
filler_data_uniq$center_condition <- myCenter(filler_data_uniq$condition)
```

Now, we rerun the linear regression.
```{r}
lin.fill.cen <- lmer(arcsin_prop_action ~ center_condition + (1|participant_id), 
            data = filler_data_uniq, REML = F)
summary(lin.fill.cen)
```

This takes care of the collinearity.

Now, we conduct a likelihood ratio test between the mixed effects linear regression model and the model without the effect of condition:
```{r}
lin.fill.base <- lmer(arcsin_prop_action ~ (1|participant_id), data = filler_data_uniq, 
                 REML = F)
summary(lin.fill.base)

anova(lin.fill.cen, lin.fill.base)
```

There is a significant main effect of condition on proportion of looks to the action video, where participants in the verb condition have a higher proportion of looks to the action video.

## Logistic regression

Now we build a mixed effects logistic regression model predicting log odds of looking towards the action video over looking towards the object video as a function of condition, with random intercepts for participant and previous look.
```{r}
lg.train <- glmer(look_action_video ~ condition + 
              previous_look_action_video + 
              (previous_look_action_video | participant_id), 
             data = train_data,
             family = "binomial")
summary(lg.train)
```


There is a high correlation between condition and the intercept as well as previous look and the intercept, so we center condition and previous look.
```{r}
train_data$center_condition <- myCenter(train_data$condition)

train_data$center_prev_look_action <- myCenter(as.numeric(train_data$previous_look_action_video))

lg.train.cen <- glmer(look_action_video ~ center_condition + center_prev_look_action + 
              (1 + center_prev_look_action | participant_id), 
             data = train_data,
             family = "binomial")
summary(lg.train.cen)
```

This reduces the collinearity.

Now, we conduct a likelihood ratio test between the logistic regression model and the model without the effect of condition:
```{r}
lg.train.base.con <- glmer(look_action_video ~ center_prev_look_action + 
              (1 + center_prev_look_action | participant_id), 
             data = train_data,
             family = "binomial")
summary(lg.train.base.con)

anova(lg.train.base.con, lg.train.cen)
```

There is a significant main effect of condition such that participants in the verb condition were more likely to look to the action video. 

We also conduct a likelihood ratio test between the logistic regression model and the model without the effect of previous gaze:
```{r}
lg.train.base.prev <- glmer(look_action_video ~ center_condition + 
              (1 | participant_id), 
             data = train_data,
             family = "binomial")
summary(lg.train.base.prev)

anova(lg.train.base.prev, lg.train.cen)
```

There is a significant main effect of previous look such that if a participant's previous look was to the action video, their next look is more likely to be to the action video as well.


## Inspect the generalization trial data

```{r}
gen_data = et_data %>% filter(descriptor_condition == "gen",
                              video_stage == "event",
                                look_left_video == TRUE | 
                                  look_right_video == TRUE)

```

Add a column for proportion of looks per participant.
```{r}
gen_data <- gen_data %>% group_by(participant_id, trial_no) %>%
  mutate(trial_prop_action = mean(look_action_video))
```

First, let's make a quick histogram of the values for proportion of looks to the action video.
```{r}
hist(unique(gen_data$trial_prop_action),
            main = "Histogram of proportion of looks to action video [GEN]",
            xlab = "Proportion of looks to action video")
```

We see that the values are quite spread out. We will repeat the original authors' analysis, in which they ArcSin-transform the proportion of looks to the action video.

Add a column with ArcSin-transformed proportion of looks toward the action video for each trial.
```{r}
gen_data <- gen_data %>% 
  mutate(arcsin_prop_action = asin(sqrt((trial_prop_action))))
```

The histogram of the transformed proportions looks much more normal.
```{r}
hist(unique(gen_data$arcsin_prop_action),
     main = "Histogram of ArcSin-transformed proportion of looks to action video",
            xlab = "ArcSin-transformed proportion of looks to action video")
```

We only need one data point per test trial per participant, so pull out this data.
```{r}
gen_data_uniq <- gen_data %>% group_by(participant_id, trial_no) %>%
  filter(row_number() == 1)
```

Now, we build a mixed effects linear model regressing ArcSin-transformed proportion of looks on condition.
```{r}
lin.gen <- lm(arcsin_prop_action ~ condition, 
            data = gen_data_uniq)
summary(lin.gen)
```

Now, we conduct a likelihood ratio test between the mixed effects linear regression model and the model without the effect of condition:
```{r}
lin.gen.base <- lm(arcsin_prop_action ~ participant_id, data = gen_data_uniq)
summary(lin.gen.base)

anova(lin.gen, lin.gen.base)
```
